---
title: "Powers"
author: "Santiago David"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Powers}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

### Description:
This package was created as part of a homework for STAT547-UBC. It is an extension of the package powers created by Vincenzo Coia
It is not intended to be a serious package, but still it is useful to calculate the 
square and cube power of a vector, and to perform Box-Cox transformations

### Functions
There are three functions on this package:

- `square()`: computes the square of a number or vector
- `cube()`: computes the cube of a number or vector
- `boxcox()`: performs Box-Cox transformation for any scalar parameter (lambda), only for positive numbers

### Examples `square()` and `cube()`
```{r}
library(powers)

#Lets create a vector
vector1 <- c(1:10)

# and now apply our function to square each element on this vector
square(vector1)

# we can also power each element to the cube
cube(vector1)
```

Now, we can also remove NA's if there is any in our vector 
```{r}
vector2 <- c(-1, 0, 1, NA, 3, NA, 5)
square(vector2)
square(vector2, na.rm = TRUE)
cube(vector2, na.rm = TRUE)
```

### Examples `boxcox()`
```{r}
# we can use our previous vector1, we have to provide a lambda parameter
boxcox(vector1, 1)
boxcox(vector1, 2)
boxcox(vector1, 0)
```

Ideally, the user should explore a range of values for lambda to find the optimal value that approximates the data to a normal distribution.

